---
title: "Meta Analysis Psilocybin Cognition"
author: "Parsa Yousefi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)a
#install.packages("readxl")
#install.packages("rmarkdown")
#install.packages("metafor")
#install.packages("meta")
#install.packages("dplyr")
#install.packages("gridExtra")

library("rmarkdown")
library('readxl')
library('metafor')
library("meta")
#install.packages("mvmeta")
#library("mvmeta")
library("dplyr")
library("ggplot2")
library("gridExtra")
source("transform_functions.r")
source("https://raw.githubusercontent.com/talgalili/R-code-snippets/master/boxplot.with.outlier.label.r")

if (!require("remotes")) {
  install.packages("remotes")
}
#remotes::install_github("guido-s/meta", ref = "R-book-first-edition")
#remotes::install_github("MathiasHarrer/dmetar")

# Define data file
datafile <- "Overview_Studies.xlsx"
```



```{r Data Preparation}
# Load necessary library
Read_Prepare <- function(datafile) {
  
  # Read and prepare data
  data_low <- as.data.frame(read_excel(datafile, sheet = "Low Dose"))
  data_mid <- as.data.frame(read_excel(datafile, sheet = "Mid Dose"))
  data_high <- as.data.frame(read_excel(datafile, sheet = "High Dose"))

  # Columns to select
  cols_to_select <- c("ID", "CognitiveFunction", "N_final", "ES_final_RT", "ES_final_ACC", 
                      "ES_final_other", "Timepoint (min)", "Dose range (Hi, Mid, Low, MD)", 
                      "PlotLabel", "DoseLabel", "EF sensitivity (1-3)")

  # Combine datasets
  data <- rbind(data_low[, cols_to_select],
                data_mid[, cols_to_select],
                data_high[, cols_to_select])

  # preprocessing
  data$ES_ID <- seq_along(data[,1])
  numeric_cols <- c("ES_ID","N_final", "ES_final_RT", "ES_final_ACC", "ES_final_other", "Timepoint (min)")
  for (col in numeric_cols) {
    if (col %in% colnames(data)) {
      data[, col] <- as.numeric(data[, col])
    }
  }
    for (col in names(data)) {
        # Check if the column is of type character
        if (is.character(data[[col]])) {
            # Remove carriage return characters
            data[[col]] <- gsub("\r", "", data[[col]])
        }
    }
    
  

  return(list(data = data, data_low = data_low, data_mid = data_mid, data_high = data_high))
}
datasets <- Read_Prepare(datafile)
data <- datasets$data
data_low <- datasets$data_low
data_mid <- datasets$data_mid
data_high <- datasets$data_high

```
```{r}

```
```{r pre vs post peak}
ClassifyTiming <- function(data, start_peak, stop_peak) {
    # Ensure 'data' is a data frame
    if(!is.data.frame(data)) {
        stop("The 'data' argument must be a data frame.")
    }

    # Check if the "Timepoint (min)" column exists in the data frame
    if(!"Timepoint (min)" %in% names(data)) {
        stop("The data frame does not contain a 'Timepoint (min)' column.")
    }

    # Initialize the 'timing' column to 0
    data$timing <- 0

    # Retrieve the "Timepoint (min)" column
    timepoint_col <- data[["Timepoint (min)"]]

    # Classify as pre-peak (coded as 0)
    data$timing[timepoint_col < start_peak] <- 0

    # Classify as post-peak (coded as 2)
    data$timing[timepoint_col > stop_peak] <- 2

    # Classify as during peak (neither pre-peak nor post-peak, coded as 1)
    data$timing[timepoint_col >= start_peak & timepoint_col <= stop_peak] <- 1

    return(data)}

data <- ClassifyTiming(data, start_peak=120,stop_peak = 180)

```


```{r code dosage}
CodeDosage <- function(data, data_low = NULL, data_mid = NULL, data_high = NULL) {
    # Check if 'data' is a data frame
    if (!is.data.frame(data)) {
        stop("The 'data' argument must be a data frame.")
    }

    # Assign default values to data_low, data_mid, and data_high if they are not provided
    if (is.null(data_low) && exists("data_low")) {
        data_low <- get("data_low")
    }
    if (is.null(data_mid) && exists("data_mid")) {
        data_mid <- get("data_mid")
    }
    if (is.null(data_high) && exists("data_high")) {
        data_high <- get("data_high")
    }

    # Code for microdosing studies
    data$micro <- ifelse(data[,"Dose range (Hi, Mid, Low, MD)"] == "Micro", TRUE, FALSE)

    # Check if dosage data frames exist before defining dosage categories
    if (!is.null(data_low) && !is.null(data_mid) && !is.null(data_high)) {
        data$dosage_cat_3 <- c(rep(1, times = nrow(data_low)),
                               rep(2, times = nrow(data_mid)),
                               rep(3, times = nrow(data_high)))
        data$dosage_cat_2 <- c(rep(1, times = nrow(data_low)),
                               rep(2, times = (nrow(data_mid) + nrow(data_high))))
    }

    # Remove the 'Dose range (Hi, Mid, Low, MD)' column
    data <- dplyr::select(data, -`Dose range (Hi, Mid, Low, MD)`)
    return(data)}
data <- CodeDosage(data, data_low, data_mid, data_high)
```


```{r unique studies in dataset} 
length(unique(data$ID))
length(data[,1])


```

###add varaince of cohens d  to the dataset
```{r}
# add the variance of the Cohen's d to the dataset
# https://stats.stackexchange.com/questions/144084/variance-of-cohens-d-statistic
# https://stats.stackexchange.com/questions/495015/what-is-the-formula-for-the-standard-error-of-cohens-d
AddCohensDVariance <- function(data) {
    # Ensure 'data' is a data frame
    if (!is.data.frame(data)) {
        stop("The 'data' argument must be a data frame.")
    }

    # Initialize variance columns with NA
    data$ES_var_RT <- NA
    data$ES_var_ACC <- NA
    data$ES_var_other <- NA

    # Define split factor
    splitfactor <- 2

    # Loop through each row to calculate variances
    for (i in 1:nrow(data)) {
        N_sum <- data$N_final[i]
        N_prod <- (data$N_final[i] / splitfactor) * (data$N_final[i] / splitfactor)
        
        # Calculating variance for each effect size
        data$ES_var_RT[i] <- (N_sum / N_prod) + (data$ES_final_RT[i]^2 / (2 * N_sum))
        data$ES_var_ACC[i] <- (N_sum / N_prod) + (data$ES_final_ACC[i]^2 / (2 * N_sum))
        data$ES_var_other[i] <- (N_sum / N_prod) + (data$ES_final_other[i]^2 / (2 * N_sum))
    }

    return(data)}

data <- AddCohensDVariance(data)
```
```{r Handle Microdosing}
#Exclude/include Microdosing
ExcludeMD <- function(data) {
    if (!is.data.frame(data)) {
        stop("The 'data' argument must be a data frame.")
    }

    # Exclude microdosing
    data_no_md <- data[data$micro != TRUE, ]

    # Return the dataset without microdosing
    return(data_no_md)
}
#data <- ExcludeMD(data)

```

###dataset after completion

```{r}
print(length(unique(data[,1])))
print(length(data[,1]))


```
```{r RT Selection}
#select RT
sel_RT  <- !is.na(data$ES_final_RT)
data_RT <- data[sel_RT, ]
# nr of ESs for RT measure
nrow(data_RT)
length(unique(data_RT$ID))
table(data_RT$timing)
```

```{r ACC Selection}

sel_ACC  <- !is.na(data$ES_final_ACC)
data_ACC <- data[sel_ACC, ]
# nr of ESs for RT measure
nrow(data_ACC)
length(unique(data_ACC$ID))
table(data_ACC$timing)

```


##Random Effect Models

```{r}
# #nested model
# mod_all_ml <- rma.mv(yi     = ES_final_RT,
#                      V      = ES_var_RT,
#                      random = ~ 1 | ID, 
#                      data   = data_RT)
# summary(mod_all_ml)


#  ### UPDATED I^2 here #######
# W <- diag(1/mod_all_ml$vi)
# X <- model.matrix(mod_all_ml)
# P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
# 100 * sum(mod_all_ml$sigma2) / (sum(mod_all_ml$sigma2) + (mod_all_ml$k-mod_all_ml$p)/sum(diag(P)))
#print(data_RT$ID)
```


```{r Meta analysis function}
calculate_meta <- function(RT=FALSE, ACC=FALSE, plot=FALSE, multilevel=TRUE) {
    
    if(RT) {
        data <- data_RT
        effect_size_col <- "ES_final_RT"
        variance_col <- "ES_var_RT"
        if(multilevel) {
            forest_title <- "Forest plot for the multilevel model of Reaction Times"
            funnel_title <- "Funnel plot for the multilevel model of Reaction Times"
            
        } else {
            forest_title <- "Forest plot for the random effects model of Reaction Times"
            funnel_title <- "Funnel plot for the random effects model of Reaction Times"
        
        }
    } else if (ACC) {
        data <- data_ACC
        effect_size_col <- "ES_final_ACC"
        variance_col <- "ES_var_ACC"
        if(multilevel) {
            forest_title <- "Forest plot for the multilevel model of Accuracy"
            funnel_title <- "Funnel plot for the multilevel model of Accuracy"
        
        } else {
            forest_title <- "Forest plot for the random effects model of Accuracy"
            funnel_title <- "Funnel plot for the random effects model of Accuracy"
        
        }
    }

    data <- data[order(data$ID), ]
    
    if(multilevel) {
        library(metafor)

        model <- rma.mv(yi = data[[effect_size_col]], 
                        V = data[[variance_col]],
                        random = ~ 1 | ID/ES_ID, 
                        data = data,
                        test = "t",
                        method = "REML"
                        )
        model_plain <- rma.mv(yi = data[[effect_size_col]], 
                        V = data[[variance_col]],
                        random = ~ 1 | ID/ES_ID,
                        data = data,
                        test = "t",
                        method = "REML",
                        sigma2 =  c(0, NA)
                        )
    
        #print("Model results non nested:")
        #print(summary(model_plain))
        print("Model results nested:")
        print(summary(model))

        I2_nested <- var.comp(model)

        print(I2_nested)
        print(I2_nested$totalI2)
        print("model comparison nested vs non-nested:")
        print(anova(model,model_plain))
        if(plot) {
            source("transform_functions.r")
            par(mfrow=c(2,1))
            I2_plot <- print(I2_nested$plot)

            data$cluster_change <- c(0, diff(data$ID))  
            data$cluster_change[data$cluster_change > 0] <- 1

            rows <- (1:nrow(data)) + cumsum(data$cluster_change * 0.3)

            op <- par(tck=-.01, mgp=c(1.6, .2, 0), mar=c(3, 8, 1, 6))

            forest(model,
                   slab = data$PlotLabel,
                   ilab = cbind(data$N_final, data$DoseLabel),
                   ilab.xpos = c(-3, -2),
                   cex = 0.9,
                   header = TRUE,
                   rows = rows,
                   ylim = c(0.5, max(rows) + 4),
                   main = forest_title)

            abline(h = rows[data$cluster_change == 1] - 0.5, lty = 2)

            par(op)
            funnel(model, main = funnel_title)
        }

    } else {
        library(metafor)

        model<- rma.mv(yi = data[[effect_size_col]], 
                        V = data[[variance_col]],
                        random = ~ 1 | ID,
                        data = data,
                        test = "t",
                        method = "REML",
                        )                    
        print(summary(model))

        if(plot) {
            par(mfrow=c(2,1))
            forest(model, 
                   slab = data$PlotLabel, 
                   ilab = cbind(data$N_final, data$DoseLabel),
                   main = forest_title)
             
            funnel(model, main = funnel_title)
        }
    }
    par(mfrow=c(1,1))  

    return(invisible(model))
}
```

```{r}

calculate_meta(ACC=TRUE, plot = TRUE,  multilevel=TRUE)
```

```{r Extreme cases}
identify_outliers <- function(data_type, multi=FALSE) {
  # Validate input
  if(data_type != "RT" && data_type != "ACC") {
    stop("data_type must be 'RT' or 'ACC'.")
  }
  
  library(ggplot2) 
  
  # Select data, call calculate_meta accordingly, and set parameters based on the input arguments
  if(data_type == "RT") {
    data <- as.data.frame(data_RT) 
    effect_size_col <- "ES_final_RT"
    variance_col <- "ES_var_RT"
    plottitle= "Reaction Time Effect Size Distribution"
    print("Analyzing outliers for Reaction Times")

  } else if (data_type == "ACC") {
    data <- as.data.frame(data_ACC)  
    effect_size_col <- "ES_final_ACC"
    variance_col <- "ES_var_ACC"
    plottitle= "Accuracy Effect Size Distribution"
    print("Analyzing outliers for Accuracy")
  }
  
  model_results <- calculate_meta(RT=data_type == "RT", ACC=data_type == "ACC", multilevel=multi)
  

  overall_ci_lb <- model_results$ci.lb
  overall_ci_ub <- model_results$ci.ub
  

  data$d <- data[[effect_size_col]]
  
  # Calculate CI for all observed effect sizes and identify outliers
  data$upperci <- data$d + 1.96 * sqrt(data[[variance_col]])
  data$lowerci <- data$d - 1.96 * sqrt(data[[variance_col]])
  data$outlier <- with(data, upperci < overall_ci_lb | lowerci > overall_ci_ub)
  
  

  pooled_effect <- model_results$beta
  
  # Plot
  plot <- ggplot(data = data, aes(x = d, colour = outlier, fill = outlier)) +
    geom_histogram(alpha = .2, position = "identity", bins = 20, binwidth = .3) + 
    geom_vline(xintercept = pooled_effect, linetype="dashed", color="blue") +
    theme_bw() +
    labs(title=plottitle, x="Effect Size", y="Frequency") +
    scale_fill_manual(values = c("FALSE" = "grey", "TRUE" = "red")) +
    scale_colour_manual(values = c("FALSE" = "black", "TRUE" = "red"))

  print(plot)

  outliers <- data[data$outlier, ]
  if(nrow(outliers) > 0) {
    print("Nr of outliers:")
    print(nrow(outliers))
  } else {
    cat("No outliers identified.\n")
  }
    filtered_data <- data[!data$outlier, ]
    model_no_outlier <- rma.mv(yi = filtered_data[[effect_size_col]], 
        V = filtered_data[[variance_col]],
        random = ~ 1 | ID/ES_ID, 
        data = filtered_data, 
        test = "t",
        method = "REML"
        )

        cat("Model results with outliers:", "G = ", round(model_results$b[1], 2),
        ", 95% CI [", round(model_results$ci.lb, 2),
        ", ", round(model_results$ci.ub, 2), "]" , sep = "")

        cat("Model results No outlier:","G = ", round(model_no_outlier$b[1], 2),
        ", 95% CI [", round(model_no_outlier$ci.lb, 2),
        ", ", round(model_no_outlier$ci.ub, 2), "]", sep = "")
  return(invisible(outliers))
}
```
```{r}

identify_outliers("RT", multi = TRUE)
```


```{r Residual inspection}
calculate_residuals <- function(RT = FALSE, ACC = FALSE, outlier_threshold = 2) {
    # Ensure that either RT or ACC is TRUE, but not both
    if (RT == TRUE && ACC == TRUE) {
        stop("Only one of RT or ACC should be TRUE")
    } else if (RT == FALSE && ACC == FALSE) {
        stop("At least one of RT or ACC should be TRUE")
    }

    # Select the appropriate data based on RT or ACC
    data_selected <- if (RT) {
        plottitle = "Reaction Time"
        calculate_meta(RT = TRUE, plot = FALSE, multilevel = TRUE)
        
    } else if (ACC) {
        plottitle = "Accuracy"
        calculate_meta(ACC = TRUE, plot = FALSE, multilevel = TRUE)
        
    }
    
    # Standardized residuals
    res_mod_all_ml <- rstandard(data_selected)
    res_mod_all_plain <- residuals(data_selected)
    # Determine the appropriate dataset for the ID
    data_for_ID <- if (RT) data_RT else data_ACC

    
    # Set up the plotting area
    par(mfrow=c(1,2))

    # Boxplot
    data_for_boxplot <- data.frame(z = res_mod_all_ml$z, ID = data_for_ID$ID)
    boxplot <- ggplot(data_for_boxplot, aes(x = "", y = z)) +
        geom_boxplot() +
        theme_gray() +
        labs(y = "Z values", title = paste("Boxplot of Standardized Residuals for", plottitle))
    # Barplot
    data_for_barplot <- data.frame(ID = data_for_ID$ID, Residuals = res_mod_all_ml$z)
    barplot <- ggplot(data_for_barplot, aes(x = ID, y = Residuals)) +
        geom_bar(stat = "identity", position = position_dodge()) +
        coord_flip() +  # To make the barplot horizontal
        theme_gray() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
        labs(x = "ID", y = "Standardized Residuals", title = paste("Barplot of Standardized Residuals for", plottitle))
    #display
    library(gridExtra)
    grid.arrange(boxplot, barplot, ncol = 1)

    #outlier handling:
    #outliers based on standardized residuals > multi_outlier
    outliers_indices <- which(abs(res_mod_all_ml$z) > outlier_threshold) 
    # Extract the corresponding rows from the dataset
    outlier_studies <- data_for_ID[outliers_indices, ]

    # outlier studies
    print(outlier_studies)
    return(invisible(res_mod_all_ml))
}

calculate_residuals(RT= TRUE, outlier_threshold = 3)


```

```{r }


```
```{r moderation}
#library(metafor)

moderation_analysis <- function(RT = FALSE, ACC = FALSE, moderation_var) {
    # Check that either RT or ACC is TRUE
    if (RT == TRUE && ACC == TRUE) {
        stop("Only one of RT or ACC should be TRUE")
    } else if (RT == FALSE && ACC == FALSE) {
        stop("AT least of RT or ACC should be TRUE")
    }

    # Select the appropriate data and columns based on RT or ACC
    if (RT) {
        data <- data_RT
        effect_size_col <- "ES_final_RT"
        variance_col <- "ES_var_RT"
    } else if (ACC) {
        data <- data_ACC
        effect_size_col <- "ES_final_ACC"
        variance_col <- "ES_var_ACC"
    }

    # Ensure the moderation variable exists in the data
    if (!moderation_var %in% names(data)) {
        stop(paste("The moderation variable", moderation_var, "is not in the dataset."))
    }

    # Convert moderation variable to a factor
    data[[moderation_var]] <- as.factor(data[[moderation_var]])

    # Running the mixed-effects model with moderation
    model <- rma.mv(yi = data[[effect_size_col]], 
                    V = data[[variance_col]],
                    random = ~ 1 | ID/ES_ID, 
                    data = data,
                    method = "REML",
                    mods = as.formula(paste0("~", moderation_var))
                   )

    # Return the summary of the model
    return(summary(model))
}
#possible moderators: CognitiveFunction. dosage_cat_3, dosage_cat_2, timing
#moderation_analysis( ACC = TRUE, moderation_var = "CognitiveFunction")
#moderation_analysis( ACC = TRUE, moderation_var = "dosage_cat_3")#low vs mid vs high
#moderation_analysis( ACC = TRUE, moderation_var = "dosage_cat_2")#low vs mid & high
#moderation_analysis( ACC = TRUE, moderation_var = "timing")




```


```{r}
#moderation_analysis( ACC = TRUE, moderation_var = )
model <- rma.mv(yi = data$ES_final_ACC, 
                V = data$ES_var_ACC,
                random = ~ 1 | factor(ID)/factor(ES_ID), 
                data = data,
                method = "REML",
                mods = as.formula("~ `EF sensitivity (1-3)`"))
summary(model)
```

```{r}
#moderation_analysis( RT = TRUE, moderation_var = )
model <- rma.mv(yi = data$ES_final_RT, 
                V = data$ES_var_RT,
                random = ~ 1 | factor(ID)/factor(ES_ID), 
                data = data,
                method = "REML",
                mods = as.formula("~ `EF sensitivity (1-3)`"))
summary(model)
```



```{r}
```

##Forestplot

```{r}

slab_vector <- paste(data_RT_no_outliers$ID, 
                     data_RT_no_outliers$PlotLabel, 
                     data_RT_no_outliers$CognitiveFunction, 
                     data_RT_no_outliers$DoseLabel, 
                     data_RT_no_outliers$`Timepoint (min)`, 
                     sep = '   ')

forest.rma(multilevel_meta(data = data_RT_no_outliers),
           data        = data_RT_no_outliers, 
           header      = T,
           addfit      = T,
           showweights = T,
           addcrea     = T,
           annotate    = T,
           xlim        = c(-17, 10), 
           col         = 'red',
           order       = order(data_RT_no_outliers$ID),
           slab        = slab_vector)


```

#funnelplot RT

```{r}
funnel(mod_all_ml_no_outliers,
       yaxis            = "vi",
       legend           = T,
       level            = c(95, 99), 
       shade            = c("white", "gray65"))


print(length(unique(data_RT$ID)))
```

##Piublication Bias #nested model w.o outlier

```{r}

ranktest(calculate_meta(RT = TRUE, plot =FALSE, multilevel = TRUE))
```

#fail safe numbers w.o outlier


```{r}
fsn(x = data_RT$ES_final_RT, 
    vi = data_RT$ES_var_RT, 
    type = "Rosenthal")
fsn(x = data_RT$ES_final_RT, 
    vi = data_RT$ES_var_RT, 
    type = "Orwin",
    target = 0.1)
fsn(x = data_RT$ES_final_RT, 
    vi = data_RT$ES_var_RT, 
    type = "Rosenberg")

```



```{r}
#nested model with outlier
ranktest(mod_all_ml)
```

#fail safe numbers with outlier

```{r}
fsn(yi     = ES_final_RT, 
    vi     = ES_var_RT,
    data   = data_RT,
    type   = "Rosenthal")            
fsn(yi     = ES_final_RT,
    vi     = ES_var_RT,
    data   = data_RT,
    type   = "Orwin",
    target = 0.1)                    
fsn(yi     = ES_final_RT,
    vi     = ES_var_RT,
    data   = data_RT,
    type   = "Rosenberg")


```
```{r}
#modified Eggers test to assess publication bias
#trim and fill deosnt work on rma.mv
mod_egger_RT <- rma.mv(yi = ES_final_RT, 
                    V = ES_var_RT, 
                    mods = ~ I(1/sqrt(ES_var_RT)), # precision as moderator
                    random = ~ 1 | ID, 
                    data = data_RT)
summary(mod_egger_RT)

```
##Moderation ###by dosage:low vs mid vs high

```{r}
(mod <- rma.mv(yi     = ES_final_RT, # low vs mid vs high
               V      = ES_var_RT, 
               random = ~ 1 | ID, 
               mods   = ~factor(dosage_cat_3), 
               data   = data_RT))


```

###by dosage:low vs mid & high

```{r}
(mod <- rma.mv(yi     = ES_final_RT, #low vs mid&high
               V      = ES_var_RT, 
               random = ~ 1 | ID, 
               mods   = ~factor(dosage_cat_2), 
               data   = data_RT))


```
```{r}
print(unique(data_RT_no_outliers$CognitiveFunction))

```

##Mdoeration RT: Pre vs during vs post peak

```{r}
(mod <- rma.mv(yi     = ES_final_RT, 
               V      = ES_var_RT, 
               random = ~ 1 | ID, 
               mods   = ~factor(timing), 
               data   = data_RT))

```

##Mdoeration RT: Cognitive fucntion category

```{r}
(mod <- rma.mv(yi     = ES_final_RT, 
               V      = ES_var_RT, 
               random = ~ 1 | ID, 
               mods   = ~factor(CognitiveFunction), 
               data   = data_RT))


```

#Analysis for Accuracy
```{r}
#select ACC
sel_ACC  <- !is.na(data$ES_final_ACC)
data_ACC <- data[sel_ACC, ]
# nr of ESs for RT measure
nrow(data_ACC)
#unique IDs
length(unique(data_ACC$ID))
```

```{r}
#nested model
multilevel_meta(data = data_ACC,effect_size_col = "ES_final_ACC", variance_col = "ES_var_ACC", id_col = "ID")

```
```{r}
(mod_ACC <- rma.mv(yi     = ES_final_ACC, 
               V      = ES_var_ACC, 
               random = ~ 1 | ID, 
               data   = data_ACC))


```
```{r}
#residuals  standardized

(res_ACC    <- rstandard(mod_ACC))
```
# boxplot residuals

```{r}
data_for_plot <- data.frame(z = res_mod_all_ml$z, ID = data_ACC$ID)

Q1 <- quantile(data_for_plot$z, 0.25)
Q3 <- quantile(data_for_plot$z, 0.75)
IQR <- Q3 - Q1
outlier_threshold_lower <- Q1 - 1.5 * IQR
outlier_threshold_upper <- Q3 + 1.5 * IQR

data_for_plot$outlier <- data_for_plot$z < outlier_threshold_lower | data_for_plot$z > outlier_threshold_upper

ggplot(data_for_plot, aes(x = "", y = z)) +
    geom_boxplot() +
    geom_text(data = filter(data_for_plot, outlier), aes(label = ID), nudge_y = 0.2) +
    theme_gray() +
    labs(y = "Z values", title = "Boxplot with Outliers Labeled")


```
# barplot residuals

```{r}
zresids <- data.frame(ID = data_ACC[,1], Residuals = rstandard(mod_ACC)$z)

# Creating a horizontal barplot
ggplot(zresids, aes(x = ID, y = Residuals)) +
        geom_bar(stat = "identity", position = position_dodge()) +
        coord_flip() +  # To make the barplot horizontal
        theme_gray() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
        labs(x = "ID", y = "Standardized Residuals", title = "Barplot of Standardized Residuals")

```
```{r}
ranktest(mod_ACC)

```
```{r}
fsn(x = data_ACC$ES_final_ACC, 
    vi = data_ACC$ES_var_ACC, 
    type = "Rosenthal")
fsn(x = data_ACC$ES_final_ACC, 
    vi = data_ACC$ES_var_ACC, 
    type = "Orwin",
    target = 0.1)
fsn(x = data_ACC$ES_final_ACC, 
    vi = data_ACC$ES_var_ACC, 
    type = "Rosenberg")
```

##Forestplot

```{r}

slab_vector <- paste(data_ACC$ID, 
                     data_ACC$PlotLabel, 
                     data_ACC$CognitiveFunction, 
                     data_ACC$DoseLabel, 
                     data_ACC$`Timepoint (min)`, 
                     sep = '   ')

forest.rma(mod_ACC,
           data        = data_ACC, 
           header      = T,
           addfit      = T,
           showweights = T,
           addcrea     = T,
           annotate    = T,
           xlim        = c(-17, 10), 
           col         = 'red',
           order       = order(data_ACC$ID),
           slab        = slab_vector)


```

#funnelplot ACC

```{r}
funnel(mod_ACC,
       yaxis            = "vi",
       legend           = T,
       level            = c(95, 99), 
       shade            = c("white", "gray65"))


print(data_ACC$ES_final_ACC)
```
```{r}
#modified Eggers test to assess publication bias
#trim and fill deosnt work on rma.mv
mod_egger_ACC <- rma.mv(yi = ES_final_ACC, 
                    V = ES_var_ACC, 
                    mods = ~ I(1/sqrt(ES_var_ACC)), # precision as moderator
                    random = ~ 1 | ID, 
                    data = data_ACC)
summary(mod_egger)
```

