---
title: "RRIP_s3648540_RT"
author: "Parsa Yousefi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)a
library("rmarkdown")
library('readxl')
library('metafor')
library("dplyr")
library("ggplot2")
source("transform_functions.r")
source("https://raw.githubusercontent.com/talgalili/R-code-snippets/master/boxplot.with.outlier.label.r")
# Define data file
datafile <- "Overview_Studies.xlsx"
```

###Data Preparation

```{r}

# Read and prepare data
data_low <- as.data.frame(read_excel(datafile, sheet= "Low Dose"))
data_mid <- as.data.frame(read_excel(datafile, sheet= "Mid Dose"))
data_high <- as.data.frame(read_excel(datafile, sheet= "High Dose"))
# Combine datasets
data <- rbind(data_low[,  c("ID", "CognitiveFunction", "N_final", "ES_final_RT", "ES_final_ACC", "ES_final_other", "Timepoint (min)", "Dose range (Hi, Mid, Low, MD)", "PlotLabel", "DoseLabel")],
              data_mid[,  c("ID", "CognitiveFunction", "N_final", "ES_final_RT", "ES_final_ACC", "ES_final_other", "Timepoint (min)", "Dose range (Hi, Mid, Low, MD)", "PlotLabel", "DoseLabel")],
              data_high[, c("ID", "CognitiveFunction", "N_final", "ES_final_RT", "ES_final_ACC", "ES_final_other", "Timepoint (min)", "Dose range (Hi, Mid, Low, MD)", "PlotLabel", "DoseLabel")])

# preprocessing
for (j in c(3,4,5,6,7))  data[,j] <- as.numeric(data[,j])

for x in data[,]
print(length(data))
```

#define pre vs post peak

```{r}
#Multiverse variables
#multi_timepoint <- list(120, 180, 240, 360)
#multi_outlier <- list(2,3)
#for item in multi_timepoint:
 # for item in multi_outlier:
data$timing <- 0
data$timing[data[,7] < 120] <- 0 # pre-peak coded as 0
data$timing[data[,7] > 180] <- 2 # post-peak coded as 2
data$timing[data[,7] >= 120 & data[,7] <= 180] <- 1 # for during peak (neither pre-peak nor post-peak), coded as 1
```


###nr of datapoints pre vs post

```{r}
table(data$timing)                    
```

```{r}
#code microdosing studies
data$micro                        <- ifelse(data[,8]=="Micro", TRUE, FALSE)
table(data$micro)
#define dosage categories
data$dosage_cat_3                 <- c(rep(1, times = nrow(data_low)),
                                       rep(2, times = nrow(data_mid)),
                                       rep(3, times = nrow(data_high)))
data$dosage_cat_2                 <- c(rep(1, times = nrow(data_low)),
                                       rep(2, times = (nrow(data_mid) + nrow(data_high))))
data <- data[,-c(8)]
```

#### this many unique studies in dataset

```{r} 
length(unique(data$ID))
summary(data)
```

```{r}
# add the variance of the Cohen's d to the dataset
# https://stats.stackexchange.com/questions/144084/variance-of-cohens-d-statistic
# https://stats.stackexchange.com/questions/495015/what-is-the-formula-for-the-standard-error-of-cohens-d
data$ES_var_RT         <- NA
data$ES_var_ACC        <- NA
data$ES_var_other      <- NA
splitfactor            <- 2
for (i in 1:nrow(data)) {
  N_sum                <-  data$N_final[i] 
  N_prod               <- (data$N_final[i]/splitfactor)*(data$N_final[i]/splitfactor)
  data$ES_var_RT[i]    <- (N_sum / N_prod) + (data$ES_final_RT[i]^2 / (2*N_sum)) # or Vdrm=(1/n+drm2/2n)2(1-r) should r be known
  data$ES_var_ACC[i]   <- (N_sum / N_prod) + (data$ES_final_ACC[i]^2 / (2*N_sum))
  data$ES_var_other[i] <- (N_sum / N_prod) + (data$ES_final_other[i]^2 / (2*N_sum))
}
```

###dataset after completion

```{r}
print(data)
```

#Analysis for RT

```{r}
sel_RT  <- !is.na(data$ES_final_RT)
data_RT <- data[sel_RT,]

# nr of ESs for RT measure
nrow(data_RT)
```

```{r}
#nr of unique studies in dataset
length(table(data_RT$ID))
table(data_RT$timing)
```

##Random Effect Models

```{r}
#nested model
mod_all_ml <- rma.mv(yi     = ES_final_RT,
                     V      = ES_var_RT,
                     random = ~ 1 | ID, 
                     data   = data_RT)
summary(mod_all_ml)


 ### UPDATED I^2 here #######
W <- diag(1/mod_all_ml$vi)
X <- model.matrix(mod_all_ml)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
100 * sum(mod_all_ml$sigma2) / (sum(mod_all_ml$sigma2) + (mod_all_ml$k-mod_all_ml$p)/sum(diag(P)))


```

##outlier handling

```{r}
#Residuals raw
(res_mod_all_plain <- rstandard(mod_all_plain))  
```

```{r}
#residuals  standardized

(res_mod_all_ml    <- rstandard(mod_all_ml))
```

# boxplot residuals

```{r}
data_for_plot <- data.frame(z = res_mod_all_ml$z, ID = data_RT$ID)

Q1 <- quantile(data_for_plot$z, 0.25)
Q3 <- quantile(data_for_plot$z, 0.75)
IQR <- Q3 - Q1
outlier_threshold_lower <- Q1 - 1.5 * IQR
outlier_threshold_upper <- Q3 + 1.5 * IQR

data_for_plot$outlier <- data_for_plot$z < outlier_threshold_lower | data_for_plot$z > outlier_threshold_upper

ggplot(data_for_plot, aes(x = "", y = z)) +
    geom_boxplot() +
    geom_text(data = filter(data_for_plot, outlier), aes(label = ID), nudge_y = 0.2) +
    theme_gray() +
    labs(y = "Z values", title = "Boxplot with Outliers Labeled")


```

# barplot residuals

```{r}
zresids <- data.frame(ID = data_RT[,1], Residuals = rstandard(mod_all_ml)$z)

# Creating a horizontal barplot
ggplot(zresids, aes(x = ID, y = Residuals)) +
        geom_bar(stat = "identity", position = position_dodge()) +
        coord_flip() +  # To make the barplot horizontal
        theme_gray() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
        labs(x = "ID", y = "Standardized Residuals", title = "Barplot of Standardized Residuals")

```

```{r}
#outliers based on standardized residuals > multi_outlier
outliers_indices <- which(abs(res_mod_all_ml$z) > multi_outlier) 
# Extract the corresponding rows from the dataset
outlier_studies <- data_RT[outliers_indices, ]

# outlier studies
print(outlier_studies) 
# Exclude these studies from the dataset
data_RT_no_outliers <- data_RT[-outliers_indices, ]

```

```{r}

###Analysis w.o outliers
#nested
mod_all_ml_no_outliers <- rma.mv(yi     = ES_final_RT,
                                 V      = ES_var_RT,
                                 random = ~ 1 | ID, 
                                 data   = data_RT_no_outliers)
summary(mod_all_ml_no_outliers)
```

```{r}
#nonnested 
mod_all_plain_no_outliers <- rma(yi     = ES_final_RT, 
                     vi     = ES_var_RT, 
                     data   = data_RT_no_outliers,
                     method = "DL")
summary(mod_all_plain_no_outliers)
```

### UPDATED I\^2 wo outliers

```{r}
W <- diag(1/mod_all_ml_no_outliers$vi)
X <- model.matrix(mod_all_ml_no_outliers)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
100 * sum(mod_all_ml_no_outliers$sigma2) / (sum(mod_all_ml_no_outliers$sigma2) + (mod_all_ml_no_outliers$k-mod_all_ml_no_outliers$p)/sum(diag(P)))

```

##Forestplot no moderator

```{r}
forest.rma(mod_all_ml_no_outliers,
           #data        = data_RT_no_outliers, 
           header      = T,
           addfit      = T,
           showweights = T,
           #addcrea     = T,
           annotate    = T,
           xlim        = c(-12, 10), 
           col         = 'red',
           order       = order(data_RT_no_outliers$ID),
           slab        = paste("(", data_RT_no_outliers$ID, ")",data_RT_no_outliers$PlotLabel, data_RT_no_outliers$CognitiveFunction, data_RT_no_outliers$DoseLabel, sep = '  '))


```

#funnelplot RT

```{r}
funnel(mod_all_ml_no_outliers,
       yaxis            = "vi",
       legend           = T,
       level            = c(95, 99), 
       shade            = c("white", "gray65"))

```

##Piublication Bias #nested model w.o outlier

```{r}

ranktest(mod_all_ml_no_outliers)
```

#fail safe numbers w.o outlier


```{r}
fsn(yi     = ES_final_RT, 
    vi     = ES_var_RT,
    data   = data_RT_no_outliers,
    type   = "Rosenthal")
fsn(yi     = ES_final_RT,
    vi     = ES_var_RT,
    data   = data_RT_no_outliers,
    type   = "Orwin",
    target = 0.1)                    
fsn(yi     = ES_final_RT,
    vi     = ES_var_RT,
    data   = data_RT_no_outliers,
    type   = "Rosenberg")            # 252 needed to go down to non-sign ES


```



```{r}
#nested model with outlier
ranktest(mod_all_ml)
```

#fail safe numbers with outlier

```{r}
fsn(yi     = ES_final_RT, 
    vi     = ES_var_RT,
    data   = data_RT,
    type   = "Rosenthal")            
fsn(yi     = ES_final_RT,
    vi     = ES_var_RT,
    data   = data_RT,
    type   = "Orwin",
    target = 0.1)                    
fsn(yi     = ES_final_RT,
    vi     = ES_var_RT,
    data   = data_RT,
    type   = "Rosenberg")


```





##Moderation ###by dosage:low vs mid vs high

```{r}
(mod <- rma.mv(yi     = ES_final_RT, # low vs mid vs high
               V      = ES_var_RT, 
               random = ~ 1 | ID, 
               mods   = ~factor(dosage_cat_3), 
               data   = data_RT_no_outliers))


```

###by dosage:low vs mid & high

```{r}
(mod <- rma.mv(yi     = ES_final_RT, #low vs mid&high
               V      = ES_var_RT, 
               random = ~ 1 | ID, 
               mods   = ~factor(dosage_cat_2), 
               data   = data_RT_no_outliers))


```

##Mdoeration: Pre vs during vs post peak

```{r}
(mod <- rma.mv(yi     = ES_final_RT, 
               V      = ES_var_RT, 
               random = ~ 1 | ID, 
               mods   = ~factor(timing), 
               data   = data_RT_no_outliers))




```

##Mdoeration: Cognitive fucntion category

```{r}
(mod <- rma.mv(yi     = ES_final_RT, 
               V      = ES_var_RT, 
               random = ~ 1 | ID, 
               mods   = ~factor(CognitiveFunction), 
               data   = data_RT_no_outliers))


```

#Analysis for Accuracy

```{r}

```
